Accelerated convergence of convective simulations using boundary value problems

### 2017-12-15 tex/bvp_paper.tex
cite to stix

\section{Introduction}
\label{sec:intro}
Natural convection occurs in the presence of disparate scales. Granules on the
solar surface have typical length scales of 1 Mm and overturn on the order of 10 minutes, whereas
the full solar convection zone spans a depth of 200 Mm, and deep motions are expected to be at very
low Mach number and constrained by the rotational timescale (1 month) of the Sun.  
However, despite these relatively short dynamical times, the scale of energy transport on the
Sun occurs on the Kelvin-Helmholtz timescale, which is nearly $3 \times 10^7$ years for the
Sun (Michael stix 2003 Solar Physics). As simulations aim to model natural convection
by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
longer than dynamical timescales \cite{Anders&Brown2017}, simulations will have to run for longer
times to thermally converge.  Furthermore, as diffusivities decrease, finer grid meshes are required
to resolve turbulent motions, and timestep sizes decrease.  The result is that high-Ra, interesting
simulations which strive to model astrophysical convective processes are crippled by the combining effects
of decreased timestep size due and increased convergence time. In order to study these systems, careful
techniques must be developed to skip past the long thermal convergence in order to study the fast convective
flows in the proper atmosphere.

>>>>

\section{Introduction}
\label{sec:intro}
Natural convection occurs in the presence of disparate scales. Granules on the
solar surface have typical length scales of 1 Mm and overturn on the order of 10 minutes, whereas
the full solar convection zone spans a depth of 200 Mm, and deep motions are expected to be at very
low Mach number and constrained by the rotational timescale (1 month) of the Sun.  
However, despite these relatively short dynamical times, the scale of energy transport on the
Sun occurs on the Kelvin-Helmholtz timescale, which is nearly $3 \times 10^7$ years for the
Sun \cite{stix2003}. As simulations aim to model natural convection
by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
longer than dynamical timescales \cite{Anders&Brown2017}, simulations will have to run for longer
times to thermally converge.  Furthermore, as diffusivities decrease, finer grid meshes are required
to resolve turbulent motions, and timestep sizes decrease.  The result is that high-Ra, interesting
simulations which strive to model astrophysical convective processes are crippled by the combining effects
of decreased timestep size due and increased convergence time. In order to study these systems, careful
techniques must be developed to skip past the long thermal convergence in order to study the fast convective
flows in the proper atmosphere.
